---
title: My Awesome Report
subtitle: With a Really Cool Subtitle
---

## Using {tibble}

Note that we have {tibble} & {knitr} already installed, thanks to our use of the `r-packages` feature to install {dplyr} and {rmarkdown} (which depend on {tibble} and {knitr}, respectively) in our `devcontainer.json` file. See @tbl-mt-cars for more information.

```{r}
#| label: tbl-mt-cars
#| tbl-cap: First few rows of mtcars
mtcars[, 1:4] |>
    head() |>
    tibble::as_tibble(rownames = "car") |>
    knitr::kable()
```

## Using {ggplot2}

Similarly, {ggplot2} is also installed. @fig-plot-mtcars displays a chart of these values.

```{r}
#| label: fig-plot-mtcars
#| fig-height: 8
#| fig-cap: A chart of mtcars
ggplot2::ggplot(
    mtcars,
    ggplot2::aes(
        x = row.names(mtcars),
        y = mpg
    )
) +
    ggplot2::geom_bar(
        stat = "identity",
        fill = "lightblue",
        color = "black"
    ) +
    ggplot2::labs(
        title = "Miles per Gallon by Car",
        x = "Car (Make & Model)",
        y = "Miles per Gallon"
    ) +
    ggplot2::coord_flip() +
    ggplot2::theme_minimal()
```

## Using mermaidjs

Lastly, we have all of the dependencies we need to include mermaidjs diagrams, thanks to the combination of using the `browserless/chrome` base Docker image and the `installChromium` option in the `quarto-cli` feature.

```{mermaid}
%%| echo: fenced
flowchart LR
    A[(Data)] --> B(["Logic (R Code)"]) --> C[[PDF Report]]
```